---
title: 'Lab 3: binomal logistic regression'
author: "Katheryn Moya"
date: "1/26/2023"
output: html_document
---

```{r setup, echo = TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(GGally)
library(jtools)
library(AICcmodavg)
```

# Pseudocode

* Examine our data (plots, tables, summary stats)
* Identify a question
* Wrangle the data
* Identify some candidate models
* Select among candidate models using AIC/BIC
* Select among candidate models using K-fold cross validation
* Select among candidate models using area under Receiver Operator Characteristic Curve

# Explore data

```{r}
GGally::ggpairs(penguins %>% select(species, bill_length_mm:sex),#colon selects all the columns between those two
        aes(color = species))
```

going to address the two species that are most similar

```{r}
class(penguins$species) #factors have different values to them
levels(penguins$species) #can then make a subset dataframe

adelie_chinstrap <- penguins %>% 
  filter(species %in% c("Adelie","Chinstrap")) %>% #using %in% instead of == because it may match it against the wrong value so we may lose rows of observations
  mutate (species = fct_drop(species)) %>%  #fct () treating it as a different kind of object
  select(-year) %>% 
  drop_na()
  
```

## Let's check out the trends across variables

```{r}
ggplot(data = adelie_chinstrap, aes(x = body_mass_g, y = flipper_length_mm)) +
  geom_point(aes(color = sex, shape = island)) +
  facet_wrap(~species)

ggplot(adelie_chinstrap, aes(x = body_mass_g, y = bill_length_mm)) +
  geom_point(aes(color = sex, shape = island)) +
  facet_wrap(~species)
```


## Let's do some binary logistic regression!

```{r}
f1 <- species ~ body_mass_g + flipper_length_mm + sex

ad_chin_blr1 <- glm(formula = f1, data = adelie_chinstrap,
                    family = 'binomal')
ad_chin_blr1
summary(ad_chin_blr1)

blr1_tidy <- tidy(ad_chin_blr1)
```

```{r}

```


